Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-21 scripts/MouseSexDiffApril20_2020.Rmd
To do: address MISSING comments

```
### Supplemental Table 4_NEW
```{r}
kable(overall2, , digits = 3) %>%
 kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

## Heterogeneity Table and Plot
### Supplemental Table 4: "Heterogeneity within groups"
 SZ: missing a desciption so far.
```{r}
kable(heterog6, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

>>>>

```
### Supplemental Table 4
MISSING table descpition. Refer to in ms.
```{r}
kable(overall2, , digits = 3) %>%
 kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

## Heterogeneity Table and Plot
### Supplemental Table 5: "Heterogeneity within groups"
 SZ: missing a desciption so far. MISSING!! Also: rearrange table structure, what does this show??
```{r}
kable(heterog6, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```
